A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-08-24 paper/authors.tex
update ms
update ms and CMD age
update starparams

\author[0000-0002-2792-134X]{J. L. Curtis}
\affiliation{Department of Astronomy, Columbia University, 550 West 120th Street, New York, NY 10027, USA}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY 10024, USA}

\author[0000-0003-1298-9699]{K. Masuda}
\affiliation{Department of Earth and Space Science, Osaka University, Osaka 560-0043, Japan}

>>>>

% Key authors:
% ... stellar rotation & the initial crossmatch
\author[0000-0002-2792-134X]{J. L. Curtis}
\affiliation{Department of Astronomy, Columbia University, 550 West 120th Street, New York, NY 10027, USA}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY 10024, USA}

% ... Kepler correlations
\author[0000-0003-1298-9699]{K. Masuda}
\affiliation{Department of Earth and Space Science, Osaka University, Osaka 560-0043, Japan}

% ... HIRES PI
\author{L. A. Hillenbrand}
\affiliation{Cahill Center for Astrophysics, California Institute of Technology, Pasadena, CA 91125, USA}

% ... RM fitting
\author[0000-0001-7409-5688]{G. Stefansson}
\affiliation{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08540, USA}

%
% PFS Collaborators
%
\author[0000-0001-8638-0320]{A. W. Howard}
\affiliation{Cahill Center for Astrophysics, California Institute of Technology, Pasadena, CA 91125, USA}
%
\author[0000-0002-0531-1073]{H. Isaacson}
\affiliation{Astronomy Department, University of California, Berkeley,
CA 94720, USA}

%
% MUSCAT3 Collaborators
%
\author[0000-0001-8511-2981]{N. Narita}
\affiliation{Komaba Institute for Science, The University of Tokyo, 3-8-1 Komaba, Meguro, Tokyo 153-8902, Japan}
\affiliation{Japan Science and Technology Agency, PRESTO, 3-8-1 Komaba, Meguro, Tokyo 153-8902, Japan}
\affiliation{Astrobiology Center, 2-21-1 Osawa, Mitaka, Tokyo 181-8588, Japan}
\affiliation{Instituto de Astrof\'{i}sica de Canarias (IAC), 38205 La Laguna, Tenerife, Spain}

\author[0000-0002-4909-5763]{A. Fukui} % afukui@g.ecc.u-tokyo.ac.jp
\affiliation{Komaba Institute for Science, The University of Tokyo, 3-8-1 Komaba, Meguro, Tokyo 153-8902, Japan}
\affiliation{Instituto de Astrof\'{i}sica de Canarias (IAC), 38205 La Laguna, Tenerife, Spain}

\author[0000-0002-5658-5971]{Masahiro Ikoma} % ikoma.masahiro@gmail.com
\affiliation{Division of Science, National Astronomical Observatory of Japan, 2-21-1 Osawa, Mitaka, Tokyo 181-8588, Japan}

\author[0000-0002-6510-0681]{M. Tamura} % motohide.tamura@nao.ac.jp
\affiliation{Department of Astronomy, University of Tokyo, 7-3-1 Hongo, Bunkyo-ku, Tokyo 113-0033, Japan}
\affiliation{Astrobiology Center, 2-21-1 Osawa, Mitaka, Tokyo 181-8588, Japan}
\affiliation{National Astronomical Observatory of Japan, 2-21-1 Osawa, Mitaka, Tokyo 181-8588, Japan}

% AO IMAGING
\author[0000-0002-2532-2853]{S. B. Howell}
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}

### 2021-08-24 paper/ms.tex
update starparams

\title{
  %Kepler 1627Ab: A 38 Million Year Old
  Kepler 1627 Ab: A 38$\,$Myr Mini-Neptune in the Kepler Field
}

@@

The ages returned by this procedure depend on the ages assumed for
each reference cluster.  We adopted a 115\,Myr age for the Pleiades,
and a 16\,Myr age for UCL \citep{dahm_2015,pecaut_star_2016}.  The age
of IC\,2602 however is the most important ingredient, since it
receives the most weight in the interpolation.  Plausible ages for
IC\,2602 span 30\,Myr to 46\,Myr, with slightly older ages being
preferred by the lithium-depletion-boundary (LDB) measurements and
younger ages by the main-sequence turn-off
\citep{stauffer_rotational_1997,dobbie_ic_2010,david_ages_2015,randich_gaiaeso_2018,bossini_age_2019,bouma_cluster_2020}.
If we were to adopt the 30\,Myr age for IC\,2602, then the \cn\ would
be $31^{+5}_{-4}$\,Myr old.  For the converse case of 46\,Myr, the
\cn\ would be $44^{+8}_{-7}$\,Myr old.  We adopt an intermediate
38\,Myr age as our reference, yielding an age for the \cn\ of
\clusterage.\footnote{Our own exploration of the PARSEC and MIST
isochrone models over a grid of ages, metallicities, and
reddenings, we yielded the best agreement for this $\approx 38\,$Myr age
as well, given ${\rm [Fe/H] = +0.1}$ and $A_V=0.2$
\citep{bressan_parsec_2012,choi_mesa_2016}.
} While detailed analyses of the LDB or main-sequence turn-off in the
\cn\ could help resolve the tension between the LDB and isochrone
ages, these are beyond our scope.

@@

%TODO: fix sizes and numbers
If the \pn\ transit signal is created by a bonafide planet,  then to
our knowledge its age would make it the youngest planet yet found by
the main Kepler mission.\footnote{The re-purposed K2 mission found two
slightly younger systems: K2-33b
\citep{David_et_al_2017,Mann_K2_33b_2016} and V1298 Tau
\citep{david_four_2019}}  A portion of the light curve is shown with
the phase-folded transit in Figure~\ref{fig:lc}.  The dominant signal
in the \texttt{PDCSAP} photometry is a quasi-periodic starspot signal
with a peak-to-peak amplitude that varies between roughly 2\% and 8\%,
depending on the degree of asymmetry in spot coverage between the
stellar hemispheres.  The starspot signal repeats every
$2.642\pm0.042$\,days, where we have adopted an uncertainty based on
the scatter observed between different portions (quarters) of the
time-series data.  The details of how we model this starspot signal to
derive the parameters of the planet are discussed in
Appendix~\ref{app:gptransit}.  The results, given in
Table~\ref{tab:posterior}, are consistent with a mini-Neptune sized
planet ($3.56\pm 0.04\,R_\oplus$) on a circular 7.2\,day orbit
($e<0.XX$), around a G8V star ($0.91 \pm 0.05 R_\odot$).  {\bf TODO
quote the eccentricity limit}

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=\textwidth]{f14.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Radii, orbital periods, and ages of known transiting
    exoplanets}.  Planets older than
    $10^9$ years are shown with gray markers.  Planets younger than a
    gigayear, with $t/\sigma_t > 3$, are shown in color.  
    \pn\ is shown with a star.
    The abnormally large radii of the youngest transiting planets
    could be explained by their primordial atmospheres not yet
    having evaporated.
    Selection effects could also be important.
    Parameters were acquired from the NASA Exoplanet Archive on July
    2, 2021.
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

%
%This study was based in part on observations at Cerro Tololo
%Inter-American Observatory at NSF's NOIRLab (NOIRLab Prop{.} ID
%2020A-0146; 2020B-0029 PI: Bouma), which is managed by the
%Association of Universities for Research in Astronomy (AURA) under a
%cooperative agreement with the National Science Foundation.
%
%
This research has made use of the Keck Observatory Archive (KOA),
which is operated by the W. M. Keck Observatory and the NASA Exoplanet
Science Institute (NExScI), under contract with the National
Aeronautics and Space Administration.
We also thank
the Keck Observatory staff, particularly {\bf A.~Doe},
for support of HIRES and remote observing.  We recognize
the importance
that the summit of Maunakea has within the indigenous
Hawaiian community, and are deeply grateful to
have the opportunity to conduct observations from this
mountain.
%

%
% The Digitized Sky Survey was produced at the Space Telescope Science
% Institute under U.S. Government grant NAG W-2166.
% Figure~\ref{fig:scene} is based on photographic data obtained using
% the Oschin Schmidt Telescope on Palomar Mountain.
%

>>>>

\title{
  %Kepler 1627Ab: A 38 Million Year Old
  %Kepler 1627 Ab:
  A 38 Million Year Old Mini-Neptune in the Kepler Field
}

@@

The ages returned by this procedure depend on the ages assumed for
each reference cluster.  We adopted a 115\,Myr age for the Pleiades,
and a 16\,Myr age for UCL \citep{dahm_2015,pecaut_star_2016}.  The age
of IC\,2602 however is the most important ingredient, since it
receives the most weight in the interpolation.  Plausible ages for
IC\,2602 span 30\,Myr to 46\,Myr, with slightly older ages being
preferred by the lithium-depletion-boundary (LDB) measurements and
younger ages by the main-sequence turn-off
\citep{stauffer_rotational_1997,dobbie_ic_2010,david_ages_2015,randich_gaiaeso_2018,bossini_age_2019,bouma_cluster_2020}.
If we were to adopt the 30\,Myr age for IC\,2602, then the \cn\ would
be $31^{+5}_{-4}$\,Myr old.  For the converse case of 46\,Myr, the
\cn\ would be $44^{+8}_{-7}$\,Myr old.  We adopt an intermediate
38\,Myr age as our reference, yielding an age for the \cn\ of
\clusterage.\footnote{Our exploration of the PARSEC and MIST
isochrone models over a grid of ages, metallicities, and
reddenings, yielded the best agreement for this $\approx 38\,$Myr age
as well, given ${\rm [Fe/H] = +0.1}$ and $A_V=0.2$
\citep{bressan_parsec_2012,choi_mesa_2016};  this preferred CMD reddening
is higher than the \citet{lallement_threedimensional_2018} value by a factor of two.
} While detailed analyses of the LDB or main-sequence turn-off in the
\cn\ could help resolve the tension between the LDB and isochrone
ages, these are beyond our scope.

@@

%TODO: fix sizes and numbers
If the \pn\ transit signal is created by a bonafide planet,  then to
our knowledge its age would make it the youngest planet yet found by
the main Kepler mission.\footnote{The re-purposed K2 mission found two
slightly younger systems: K2-33b
\citep{David_et_al_2017,Mann_K2_33b_2016} and V1298 Tau
\citep{david_four_2019}}  A portion of the light curve is shown with
the phase-folded transit in Figure~\ref{fig:lc}.  The dominant signal
in the \texttt{PDCSAP} photometry is a quasi-periodic starspot signal
with a peak-to-peak amplitude that varies between 2\% and 8\%,
depending on the degree of asymmetry in spot coverage between the
stellar hemispheres.  The starspot signal repeats every
$2.642\pm0.042$\,days, where we have adopted an uncertainty based on
the scatter observed between different Kepler quarters.
The details of how we model this starspot signal to
derive the parameters of the planet are discussed in
Appendix~\ref{app:gptransit}.  The stellar parameters are listed
in Table~\ref{tab:starparams}; the stellar mass, radius, and effective
temperature are found by interpolating against a 38$\,$Myr MIST
isochrone.  The systematic uncertainties are taken to be the
difference in parameters from the PARSEC isochrones, and the reported
uncertainties are a quadrature sum of the statistical and systematic
components.  The transit-fitting results, given in
Table~\ref{tab:posterior}, are consistent with a mini-Neptune sized
planet ($3.56\pm 0.04\,R_\oplus$) on a circular 7.2\,day orbit
($e<0.XX$), around a G8V star ($0.88 \pm 0.02 R_\odot$).  {\bf TODO
quote the eccentricity limit}

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=\textwidth]{f14.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Radii, orbital periods, and ages of known transiting
    exoplanets}.  Planets older than
    $10^9$ years are shown with gray markers.  Planets younger than a
    gigayear, with $t/\sigma_t > 3$, are shown in color.  
    \pn\ is shown with a star.
    The abnormally large radii of the youngest transiting planets
    could be explained by their primordial atmospheres not yet
    having evaporated; direct measurements of the atmospheric outflows
    or planetary masses would help to confirm this picture.
    Selection effects may also be important.
    Parameters are from the NASA Exoplanet Archive (July
    2, 2021).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

%
%This study was based in part on observations at Cerro Tololo
%Inter-American Observatory at NSF's NOIRLab (NOIRLab Prop{.} ID
%2020A-0146; 2020B-0029 PI: Bouma), which is managed by the
%Association of Universities for Research in Astronomy (AURA) under a
%cooperative agreement with the National Science Foundation.
%
%
This research has made use of the Keck Observatory Archive (KOA),
which is operated by the W. M. Keck Observatory and the NASA Exoplanet
Science Institute (NExScI), under contract with the National
Aeronautics and Space Administration.
We also thank
the Keck Observatory staff, particularly {\bf A.~Doe},
for support of HIRES and remote observing.  We recognize
the importance
that the summit of Maunakea has within the indigenous
Hawaiian community, and are deeply grateful to
have the opportunity to conduct observations from this
mountain.
%
This paper is based in part on observations made with the MuSCAT3
instrument, developed by the Astrobiology Center and under financial
supports by JSPS KAKENHI (JP18H05439) and JST PRESTO (JPMJPR1775), at
Faulkes Telescope North on Maui, HI, operated by the Las Cumbres
Observatory.
%
This work is partly supported by JSPS KAKENHI Grant Numbers 22000005,
JP15H02063, JP17H04574, JP18H05439, JP18H05442, JST PRESTO Grant
Number JPMJPR1775, the Astrobiology Center of National Institutes of
Natural Sciences (NINS) (Grant Number AB031010).
%
% The Digitized Sky Survey was produced at the Space Telescope Science
% Institute under U.S. Government grant NAG W-2166.
% Figure~\ref{fig:scene} is based on photographic data obtained using
% the Oschin Schmidt Telescope on Palomar Mountain.
%
